Hrvatska u kontekstu europskih konvergencijskih klubova

### 2024-09-17 Paper.Rmd
weiter

```{r libs,  echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
#### LIBS ----
library(eurostat)
library(tidyverse)
library(zoo)
library(scales)
library(tseries)
library(urca)
library(fracdiff)
library(arfima)
library(gt)
library(kableExtra)
library(urca)

@@

@@

```{r fracr3 ,  echo=FALSE, message=FALSE, warning=FALSE,  fig.width=10, fig.height=6}
# Define the P-GPH estimator function
pgph_test_results <- function(data, group_name) {
  # Run the Phillips-Perron test (as a proxy for P-GPH)
  result <- ur.pp(data$diff_log_gdp_per_capita, type = "Z-alpha", model = "trend")

>>>>

```{r libs,  echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
#### LIBS ----
library(eurostat)
library(tidyverse)
library(zoo)
library(scales)
library(tseries)
library(urca)
library(fracdiff)
library(arfima)
library(gt)
library(kableExtra)

@@

```{r}
# Define a function to perform the fractional integration test and extract key stats
perform_fractional_integration <- function(data, column, group_name) {
  # Extract the specified column for testing
  log_diff <- data[[column]]

  # Apply the fracdiff function to estimate the fractional differencing parameter
  fd_result <- fracdiff(log_diff)

  # Extract the differencing parameter (d) and standard error
  d_estimate <- fd_result$d
  d_std_error <- sqrt(diag(fd_result$cov))[1]

  # Prepare a row of results for this group
  result_row <- tibble(
    group = group_name,
    d_estimate = d_estimate,
    d_std_error = d_std_error
  )

  return(result_row)
}

# Now, apply the function to each dataset and bind the results together into a summary table
fd_result_nms8 <- perform_fractional_integration(diff_croatia_vs_nms8, "diff_log_gdp_per_capita", "NMS8")
fd_result_nms12 <- perform_fractional_integration(diff_croatia_vs_nms12, "diff_log_gdp_per_capita", "NMS12")
fd_result_se4 <- perform_fractional_integration(diff_croatia_vs_se4, "diff_log_gdp_per_capita", "SE4")
fd_result_eu15 <- perform_fractional_integration(diff_croatia_vs_eu15, "diff_log_gdp_per_capita", "EU15")

# Combine results into a single table
fractional_integration_summary <- bind_rows(fd_result_nms8, fd_result_nms12, fd_result_se4, fd_result_eu15)

# Display the summary table
print(fractional_integration_summary)

@@

```{r fracr3 ,  echo=FALSE, message=FALSE, warning=FALSE,  fig.width=10, fig.height=6}

perform_gph <- function(data, column, group_name) {
  # Extract the specified column for testing
  log_diff <- data[[column]]

  # Define the Fourier frequencies and compute periodogram
  n <- length(log_diff)
  m <- floor(n^0.5)  # Choose the number of frequencies based on the rule of thumb
  freqs <- 2 * pi * (1:m) / n
  periodogram <- abs(fft(log_diff)[2:(m+1)])^2 / n

  # Perform the log-periodogram regression to estimate d
  log_periodogram <- log(periodogram)
  regression <- lm(log_periodogram ~ log(freqs))

  # Extract the fractional differencing parameter d
  d_estimate <- -regression$coefficients[2] / 2

  # Prepare a row of results for this group
  result_row <- tibble(
    group = group_name,
    d_estimate = d_estimate,
    d_std_error = NA  # No easy standard error estimation in basic GPH
  )

  return(result_row)
}

# Apply the function to your datasets
fd_result_nms8_gph <- perform_gph(diff_croatia_vs_nms8, "diff_log_gdp_per_capita", "NMS8")
fd_result_nms12_gph <- perform_gph(diff_croatia_vs_nms12, "diff_log_gdp_per_capita", "NMS12")
fd_result_se4_gph <- perform_gph(diff_croatia_vs_se4, "diff_log_gdp_per_capita", "SE4")
fd_result_eu15_gph <- perform_gph(diff_croatia_vs_eu15, "diff_log_gdp_per_capita", "EU15")

# Combine results into a single table
fractional_integration_summary_gph <- bind_rows(fd_result_nms8_gph, fd_result_nms12_gph, fd_result_se4_gph, fd_result_eu15_gph)

# Display the summary table
print(fractional_integration_summary_gph)
```

```{r fracr4 ,  echo=FALSE, message=FALSE, warning=FALSE,  fig.width=10, fig.height=6}
# Define the P-GPH estimator function
pgph_test_results <- function(data, group_name) {
  # Run the Phillips-Perron test (as a proxy for P-GPH)
  result <- ur.pp(data$diff_log_gdp_per_capita, type = "Z-alpha", model = "trend")
